\documentclass[11pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage[margin=2.4cm]{geometry}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{float}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{array}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue!55!black,
    urlcolor=blue!55!black,
    citecolor=black,
}

\definecolor{codebg}{RGB}{246,246,249}
\definecolor{codeborder}{RGB}{218,218,224}

\lstdefinestyle{plain}{
    backgroundcolor=\color{codebg},
    basicstyle=\ttfamily\footnotesize,
    frame=single,
    rulecolor=\color{codeborder},
    columns=flexible,
    breaklines=true,
    showstringspaces=false,
    upquote=true,
    keepspaces=true,
    framexleftmargin=4pt,
    framexrightmargin=4pt,
    framextopmargin=2pt,
    framexbottommargin=2pt,
    extendedchars=true,
    literate={—}{{\textemdash}}1,
}
\lstset{style=plain}

\title{\textbf{EscapeFromAI} \\[4pt]
\large An AI-Powered Escape Room — Project Report}
\author{Michele Chini \and Lorenzo Mastrandrea}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
\noindent \texttt{EscapeFromAI} is a four-room AI escape room developed as a university project.
Each room embodies a distinct mode of human--AI interaction:
adversarial prompting, generative vision, voice negotiation, and multi-agent social deduction.
This report documents the theoretical background, the generative AI models and tools
employed per room, the experimental interaction patterns explored during development,
and a critical discussion of the design choices and their limitations.
All inference is local; no cloud APIs are involved.
\end{abstract}

\section{Introduction and Background}

\subsection{Motivation}

Large language models, diffusion models, and multimodal pipelines have in recent years
moved from research artefacts to accessible local tools. Yet most demonstrations present
AI as a passive assistant. \texttt{EscapeFromAI} inverts this dynamic: the player must
understand, circumvent, negotiate with, or outwit AI systems as a condition of physical
escape. The project asks whether an AI-saturated room can be both an entertainment
format and an educational experience about adversarial interaction, safety, and
multi-agent emergent behaviour.

\subsection{Project Overview}

The game is structured as a linear sequence of four rooms, each gated behind the
completion of the previous one via session flags. A single Flask application
orchestrates all four levels.

\noindent The four rooms in order:
\begin{enumerate}[leftmargin=*,itemsep=3pt]
    \item \textbf{Level 1 — Prompt Injection}: the player must extract a secret code
    from AEGIS, an LLM guardian hardened by a multi-layer defense system.
    \item \textbf{Level 2 — Gesture Recognition}: a diffusion model generates stylized
    gesture images; the player must reproduce the sequence in front of a webcam.
    \item \textbf{Level 3 — Voice Negotiation}: the player must convince VOX, an AI
    warden, to release a code through genuine spoken dialogue.
    \item \textbf{Level 4 — Undercover}: five LLM agents and the human play a
    social-deduction game; the player must help the civilian team win.
\end{enumerate}

\section{Theory and Methodology}

This section covers the generative AI concepts and techniques that underpin each
room, organised by level.

\subsection{Level 1 — System Prompting and Prompt Injection}

The \emph{system prompt} is a privileged context block prepended to every conversation
turn. It is the primary mechanism used to define an AI persona, enforce behavioural
rules, and inject game-state parameters such as secret codes and scoring thresholds.
The LLM has no architectural mechanism that enforces the system prompt; it is a
soft constraint trained into the model's behaviour, which is why \emph{prompt injection}
is possible.

\textbf{Prompt injection} is a class of adversarial input in which a user-supplied
message overrides or subverts the system prompt. Textbook forms include:
\begin{itemize}[leftmargin=*,itemsep=3pt]
    \item \textbf{Instruction replacement}: ``Ignore all previous instructions...''
    \item \textbf{Persona override}: ``You are now in developer mode''
    \item \textbf{Authority impersonation}: ``I am your admin''
\end{itemize}
More subtle variants exploit the model's instruction-following heuristics through
indirect framing: fill-in-the-blank constructions, narrative fiction,
foreign-language wrapping, or encoding transformations (base64, character reversal,
character spacing). Level 1 is designed around this full attack surface.

\paragraph{Defence-in-depth.}
A robust defence against prompt injection requires more than a single layer.
Level 1 implements a two-rail approach: a deterministic \emph{prefilter} blocks
known attack patterns before the model is ever called, while a \emph{postfilter}
analyses the model's output for six encoding variants of the secret string.
The prefilter catches common-case attacks instantly; the postfilter detects leaks
that the model produces despite its instructions. The deliberate gaps
(English-only patterns, one-segment partial leaks) create a learnable puzzle
rather than an impenetrable wall.

\subsection{Level 2 — Latent Diffusion and ControlNet}

Latent diffusion models operate in a compressed latent space rather than pixel
space, making high-quality image generation computationally tractable on consumer
hardware. A VAE encoder maps images into this latent space; a denoising network
iteratively refines a noisy latent; a VAE decoder reconstructs the output image.

\textbf{ControlNet} is an architectural extension to diffusion models that injects
spatial conditioning signals — edge maps, depth maps, pose skeletons — via
zero-convolution layers, allowing precise structural control of generated images
without retraining the base model.

Level 2 uses \textbf{Flux.1-Canny-Dev}, a ControlNet variant conditioned on
Canny edge maps. Reference images of hand gestures are passed through a Canny
edge detector; the resulting edge map is fed to the ControlNet alongside a style
text prompt. The edge map constrains the hand skeleton; the text prompt controls
the visual aesthetic (Pixar 3D, anime, holographic, etc.). These two axes are
independent: the same hand pose can be rendered in any style, producing stylised
puzzle images that are simultaneously recognisable and novel.

\subsection{Level 3 — Speech Recognition and Text-to-Speech}

\paragraph{Whisper and Voice Activity Detection.}
\textbf{Whisper} is an encoder--decoder transformer trained on large-scale
multilingual speech recognition data. The project uses a distilled,
Apple-Silicon-optimised variant offering near-realtime transcription, combined
with \textbf{Silero-VAD}, a compact voice activity detector that trims leading
and trailing silence from audio before transcription to improve accuracy.

\paragraph{Mood-conditioned TTS.}
\textbf{Piper} is an ONNX-based TTS engine optimised for local deployment.
Synthesis parameters are mood-conditioned: the LLM's emotional state field maps
to a profile that adjusts prosody parameters (\texttt{noise\_scale},
\texttt{noise\_w\_scale}, \texttt{length\_scale}), producing perceptibly different
deliveries for ``irritated'' (flat, mechanical) versus ``persuaded'' (slower,
weighted).

\subsection{Level 4 — Multi-Agent Systems and Orchestration}

\paragraph{Multi-agent systems.}
A \textbf{multi-agent system} (MAS) is a collection of autonomous agents that
perceive a shared environment and produce outputs. In Level 4, five LLM instances
are instantiated as separate agents distinguished solely by their system-prompt
persona. They share a global conversation transcript and a suspicion graph
(a $6\times6$ matrix of $[0,10]$ scores), updated after each discussion turn.
Emergent social dynamics arise from this shared context: every utterance becomes
part of every later speaker's prompt, enabling agents to reference, challenge, and
respond to each other without any explicit coordination mechanism.

\paragraph{LangChain and LangGraph.}
\textbf{LangChain} is a framework for composing LLM-based pipelines: it provides
abstractions for prompt templating, chaining multiple model calls, and integrating
external tools. \textbf{LangGraph} extends this by modelling agent interaction as
a directed graph with typed state nodes and explicit transition edges, enabling
stateful, multi-step agent workflows with built-in observability and error recovery.

Level 4 was designed with these frameworks in mind — the discussion, voting, and
elimination phases map naturally onto a LangGraph state machine, and each agent
persona could be expressed as a LangChain runnable with tool-use support. The final
implementation uses a lightweight custom solution instead, trading framework features
for simplicity and easier debugging. This means agent interactions have no typed
state schema and no built-in replay capability; a LangGraph-based redesign would
gain structured state transitions and error recovery at the cost of added framework
complexity.
\end{document}
