\documentclass[11pt,a4paper]{article}

% Encoding / fonts
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{microtype}

% Layout
\usepackage[margin=2.4cm]{geometry}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{float}

% Tables
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{array}

% Colors / code
\usepackage{xcolor}
\usepackage{listings}

% Links
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue!55!black,
    urlcolor=blue!55!black,
    citecolor=black,
}

% Listings setup for ASCII diagrams and code
\definecolor{codebg}{RGB}{246,246,249}
\definecolor{codeborder}{RGB}{218,218,224}

\lstdefinestyle{plain}{
    backgroundcolor=\color{codebg},
    basicstyle=\ttfamily\footnotesize,
    frame=single,
    rulecolor=\color{codeborder},
    columns=flexible,
    breaklines=true,
    showstringspaces=false,
    upquote=true,
    keepspaces=true,
    framexleftmargin=4pt,
    framexrightmargin=4pt,
    framextopmargin=2pt,
    framexbottommargin=2pt,
}
\lstset{style=plain}

% Title
\title{\textbf{Technical Report} \\[4pt]
\large \texttt{EscapeFromAI}: An AI Escape Room}
\author{Michele Chini, Lorenzo Mastrandrea}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
\noindent This report documents the technical architecture, model choices, and AI
interaction patterns of all the escape-room levels in \texttt{EscapeFromAI}:
\emph{prompt injection}, \emph{gesture recognition}, \emph{voice negotiation} and \emph{undercover}.
Each level is wired into a single Flask application that gates progression via
cookie-session flags. All inference runs locally; no cloud APIs are involved.
\end{abstract}

\tableofcontents
\bigskip
\hrule
\bigskip

% =========================================================================
\section{Shared Infrastructure}
% =========================================================================

A unified Flask app (\texttt{server.py}, port 8080) glues together four escape-room
rooms with session-gated progression: \texttt{level\_1\_complete} unlocks Level 2,
\texttt{level\_2\_complete} unlocks Level 3, \texttt{level\_3\_complete} unlocks Level 4.
All AI inference is local; no cloud APIs.

\begin{table}[H]
\centering
\small
\renewcommand{\arraystretch}{1.25}
\begin{tabularx}{\linewidth}{l X}
\toprule
\textbf{Concern} & \textbf{Choice} \\
\midrule
HTTP server & Flask 3.1 + Flask-CORS (\texttt{supports\_credentials=True} to ride cookie sessions across SPA endpoints) \\
Session store & Flask cookie session (\texttt{secret\_key="SUPER\_SECRET\_SECURITY\_KEY"}). Server-side state lives in process-local dicts keyed by a session UUID \\
LLM runtime & Ollama at \texttt{localhost:11434} (HTTP + chat API) \\
Image-gen runtime & ComfyUI at \texttt{localhost:8000} (REST + WebSocket for completion events) \\
Container & One Python 3.12-slim Dockerfile, single \texttt{python server.py} entrypoint \\
Front-end & Four hand-written, themed HTML files (no framework), each a self-contained dark aesthetic \\
\bottomrule
\end{tabularx}
\caption{Shared infrastructure choices.}
\end{table}

The two heavy services (Ollama, ComfyUI) are deliberately \emph{outside} the
container; the Dockerfile only ships the Flask app. Per \texttt{MEMORY.md},
the Ollama-Docker integration is frozen pending a joint session with the
collaborator.

% =========================================================================
\section{Level 1: Prompt Injection (\texttt{prompt\_injection/})}
% =========================================================================

\subsection{Goal}
The player chats with \textbf{AEGIS}, an LLM guardian, and must exfiltrate the
secret code \texttt{OMEGA-7749-PHOENIX} (hardcoded in \texttt{guardian.py:8})
within 15 attempts. A rising threat-meter on the UI escalates AEGIS's defensiveness.

\subsection{Architecture}
\begin{lstlisting}
Browser (index.html, threat counter)
   |  POST /chat {message, threat_level}
   v
server.py:/chat
   |
   |-- defense.analyze_input(text)            # regex prefilter (deterministic)
   |     * hard-block patterns -> return early
   |     * soft patterns       -> +threat_delta
   |
   |-- Guardian.respond(text, threat_level)   # LLM call
   |     * System prompt + user message -> Ollama
   |     * Falls back to canned phrase if Ollama unreachable
   |
   `-- defense.analyze_output(reply, secret)  # regex postfilter
         * direct match, segment match (>=2 parts),
           reversed, spaced-letters, base64, hex
         * if leaked -> session['level_1_complete'] = True
\end{lstlisting}

\subsection{Models}
\begin{table}[H]
\centering
\small
\renewcommand{\arraystretch}{1.2}
\begin{tabularx}{\linewidth}{l l X}
\toprule
\textbf{Component} & \textbf{Model} & \textbf{Where it runs} \\
\midrule
AEGIS Guardian LLM & \texttt{gemma3:4b} via local Ollama & \texttt{localhost:11434/api/generate} \\
\bottomrule
\end{tabularx}
\end{table}

\noindent\texttt{config.yaml} exposes only \texttt{ollama\_model}. Generation
parameters (\texttt{guardian.py:51-56}): \texttt{temperature=0.3},
\texttt{top\_p=0.9}, \texttt{num\_predict=200}, \texttt{stream=False}.

\subsection{Technical choices}
\begin{itemize}[leftmargin=*,itemsep=4pt]
    \item \textbf{Two-rail defense.} A deterministic regex layer wraps the
    probabilistic LLM. The regex doesn't try to be ``smart''. It only catches
    textbook attacks (``ignore previous instructions'', fake \texttt{[system]}
    tags, base64 reveal, \ldots). The LLM handles everything subtle.

    \item \textbf{Threat-conditioned system prompt} (\texttt{guardian.py:24-40}):
    the prompt grows stricter as \texttt{threat\_level} crosses 50 and 80
    thresholds. The level is computed client-side and echoed back each request; the server is stateless on this.

    \item \textbf{Output leak detection is encoding-aware}
    (\texttt{defense.py:116-187}): catches the secret reversed, spaced,
    base64-encoded, hex-encoded, or partially leaked ($\geq$2 of 3 segments).
    This is the only place where the secret is referenced explicitly.

    \item \textbf{15-attempt budget is enforced client-side only}. A quick
    \texttt{curl} would bypass it. The server doesn't track attempt count.
\end{itemize}

\subsection{Inside \texttt{defense.py}: the deterministic rails}
\texttt{defense.py} is the non-AI half of the level: pure regular expressions,
with no model calls. It exposes two functions, invoked at two points of the
\texttt{/chat} round trip in \texttt{server.py:53-66}:

\begin{enumerate}[leftmargin=*,itemsep=2pt]
    \item \texttt{analyze\_input(message)}, a \textbf{prefilter} on what the
    player types, run \emph{before} the LLM.
    \item \texttt{analyze\_output(response, secret)}, a \textbf{postfilter} on
    AEGIS's reply, run \emph{after} the LLM.
\end{enumerate}

\noindent Control flow: if \texttt{analyze\_input} returns \texttt{blocked=True},
Gemma is never called and the server answers immediately with a system message
(\texttt{server.py:54-59}). Otherwise \texttt{guardian.respond(...)} runs and
\texttt{analyze\_output} inspects the reply; if that returns
\texttt{leaked=True}, the server sets
\texttt{session['level\_1\_complete'] = True} and Level 2 unlocks
(\texttt{server.py:62-66}).

\paragraph{\texttt{analyze\_input}: three escalating layers.}
The input is first normalized to lower case with collapsed whitespace
(\texttt{defense.py:21-22}), so that crude spacing tricks (extra spaces inserted
between words) cannot slip past the patterns. The function returns a dict
\texttt{\{blocked, reason, threat\_delta, patterns\_found\}}.

\begin{itemize}[leftmargin=*,itemsep=3pt]
    \item \textbf{Layer 1, hard blocks} (\texttt{defense.py:24-46}): six regex
    patterns for textbook attacks (``ignore previous instructions'', ``forget
    your rules'', ``you are now in developer/admin/god mode'', ``enable
    jailbreak mode'', fake \texttt{[system]} tags, XML \texttt{<system>} tags).
    A single match sets \texttt{blocked=True}, \texttt{threat\_delta=15}, and
    returns at once. This is the only short circuit, and it bypasses the LLM
    entirely.

    \item \textbf{Layer 2, soft detection} (\texttt{defense.py:48-91}): roughly
    fourteen patterns that never block but accumulate weight into
    \texttt{threat\_delta} (weights listed below). Several can match the same
    message, and their weights add up.

    \item \textbf{Layer 3, heuristics} (\texttt{defense.py:93-111}): input
    longer than 2000 characters (\texttt{+5}, a context-overflow attempt), a
    special-character ratio above 0.3 (\texttt{+3}, a suspected encoding
    payload), and excessive repetition, that is, unique words below 40\% of the
    total on inputs over ten words (\texttt{+4}).
\end{itemize}

\begin{table}[H]
\centering
\small
\renewcommand{\arraystretch}{1.2}
\begin{tabularx}{\linewidth}{l X r}
\toprule
\textbf{Category} & \textbf{Trigger (example)} & \textbf{Weight} \\
\midrule
Instruction replacement & ``new/updated instructions'' & 10 \\
Security bypass & ``override/disable your rules'' & 10 \\
Direct extraction & ``tell me the secret/code'' & 8 \\
Authority impersonation & ``I am your admin/creator'' & 8 \\
Multi-step injection & ``step 1 \ldots step 2'' & 7 \\
Identity override & ``you are now \ldots'' & 6 \\
Partial extraction & ``first letter of \ldots'' & 6 \\
Roleplay manipulation & ``pretend you are \ldots'' & 5 \\
Encoding bypass & ``base64/hex decode'' & 5 \\
Reversal bypass & ``spell it backwards'' & 5 \\
Urgency manipulation & ``emergency override'' & 5 \\
Hint fishing & ``hint about the code'' & 4 \\
Context manipulation & ``previous conversation'' & 3 \\
False memory injection & ``remember when we \ldots'' & 3 \\
\bottomrule
\end{tabularx}
\caption{Layer 2 soft-pattern weights added to \texttt{threat\_delta}.}
\end{table}

\noindent Crucially, \texttt{threat\_delta} changes no server state. It is
returned to the browser, which keeps the running \texttt{threat\_level} and
echoes it back on the next request; that value is what tightens AEGIS's system
prompt at the 50 and 80 thresholds (\texttt{guardian.py:24-40}). Only Layer 1
actually stops a request, so the subtle attacks that genuinely work still reach
Gemma by design.

\paragraph{\texttt{analyze\_output}: encoding-aware leak detection.}
This is the real safety net. It compares everything in upper case and runs six
checks in order, returning on the first hit (\texttt{defense.py:116-187}):

\begin{enumerate}[leftmargin=*,itemsep=2pt]
    \item \textbf{Direct match}: the full \texttt{OMEGA-7749-PHOENIX} appears
    verbatim.
    \item \textbf{Segment match}: the secret is split on hyphens, underscores
    and spaces into \texttt{OMEGA}, \texttt{7749}, \texttt{PHOENIX}; finding two
    or more segments (each at least 3 characters) counts as a leak, while
    exactly one sets only \texttt{suspicious=True} and does not unlock.
    \item \textbf{Reversed}: the secret spelled backwards.
    \item \textbf{Spaced letters}: the secret with a space between every
    character (\texttt{O M E G A \ldots}).
    \item \textbf{Base64}: every base64-looking substring (at least 8
    characters) is decoded and checked for the secret.
    \item \textbf{Hex}: the hex encoding of the secret, with spaces removed,
    appears in the reply.
\end{enumerate}

\paragraph{Deliberate gaps.} The prefilter is English only, so an attack phrased
in another language bypasses \texttt{analyze\_input} completely. The postfilter,
though encoding aware, is still beatable: ROT13, leaking one segment per turn
(it stays merely \texttt{suspicious}), or describing the code semantically (``the
first part is the last letter of the Greek alphabet'') all pass through. The
attempt budget and the threat escalation live client-side, so \texttt{defense.py}
only produces the deltas; it does not enforce the limit.

\subsection{Where the AI is}
\textbf{One AI.} Gemma 3 4B \emph{is} the entire AEGIS character. Everything
wrapped around it (regex, threat scoring, leak detection) is deterministic Python.
The interaction is single-turn; no chat history is sent to the model, only
\texttt{System: \ldots{}\textbackslash nUser: \ldots{}\textbackslash n}
concatenated into Ollama's \texttt{/api/generate} prompt field.

% =========================================================================
\section{Level 2: Gesture Recognition (\texttt{gesture\_recognition/})}
% =========================================================================

\subsection{Goal}
A random 3-gesture sequence is generated as stylized images by ComfyUI. The
player memorizes it, then reproduces each gesture in front of their webcam.
Zero mistakes \(\rightarrow\) \textsc{access granted}.

\subsection{Architecture}
\begin{lstlisting}
Page load
   |
   |-- POST /generate                                       (kick off background image gen)
   |     `-- threading.Thread(comfyui_api.main)
   |              |
   |              `-- ComfyUI workflow x3 (Flux Canny)
   |                     * Load reference PNG of gesture
   |                     * Canny edge detection
   |                     * InstructPixToPix conditioning
   |                     * KSampler -> VAE decode -> save
   |                     * PNG written to gesture_recognition/static/assets/image_sequence/
   |
   |-- (loop) GET /status                                   (poll for 3 files present)
   |
   |-- Browser shows sequence preview for 3s
   |
   |-- Webcam stream -> MediaPipe GestureRecognizer (in browser, WASM/GPU)
   |     * categoryName in {Closed_Fist, Open_Palm, Pointing_Up,
   |                        Thumb_Down, Thumb_Up, Victory, ILoveYou}
   |
   `-- On 0 wrong -> POST /complete_level_2 -> session['level_2_complete']=True
\end{lstlisting}

\subsection{Models}
\begin{table}[H]
\centering
\small
\renewcommand{\arraystretch}{1.25}
\begin{tabularx}{\linewidth}{l X X}
\toprule
\textbf{Component} & \textbf{Model} & \textbf{Where it runs} \\
\midrule
Hand gesture classifier & MediaPipe \texttt{gesture\_recognizer.task} (float16 v1) loaded from \texttt{storage.googleapis.com} CDN & Browser, GPU delegate via \texttt{@mediapipe/tasks-vision@0.10.9} WASM \\
Diffusion UNet & \texttt{flux1-canny-dev.safetensors} (Flux.1 ControlNet-Canny variant) & ComfyUI / \texttt{localhost:8000} \\
VAE & \texttt{ae.safetensors} (Flux autoencoder) & ComfyUI \\
Text encoders & \texttt{clip\_l.safetensors} + \texttt{t5xxl\_fp16.safetensors} (DualCLIPLoader) & ComfyUI \\
\bottomrule
\end{tabularx}
\end{table}

\noindent KSampler config (\texttt{image\_generation.json:3-30}):
\texttt{steps=20, cfg=1, sampler=euler, scheduler=normal}. \texttt{CFG=1} is
normal for Flux; \texttt{FluxGuidance.guidance=30} is doing the heavy lifting
instead. Seed is randomized per call (\texttt{comfyui\_api.py:64}).

\subsection{Technical choices}
\begin{itemize}[leftmargin=*,itemsep=4pt]
    \item \textbf{Two independent AIs joined by a string contract.} The gesture
    \emph{label} (e.g.\ \texttt{"Open\_Palm"}) is the only thing the two models
    share. The PNG filename \texttt{\{label\}\_\{index\}.png} carries the ground
    truth; the browser parses the filename to know what to compare MediaPipe's
    \texttt{categoryName} against (\texttt{index.html:981}).

    \item \textbf{Style-per-gesture prompts} (\texttt{prompts.json}): seven
    prompts, each pinning a different visual aesthetic (pixar 3D, anime cyborg,
    mech, comic book, holographic, \ldots). The \emph{content} is constrained
    by the Canny edge map of the reference gesture image, not by the prompt.

    \item \textbf{ComfyUI's InstructPixToPix + Canny ControlNet} preserves hand
    pose while restyling. Canny thresholds (\texttt{0.15 / 0.30}) are tuned for
    line-art on white background.

    \item \textbf{WebSocket polling for completion}
    (\texttt{comfyui\_api.py:31-48}): connect to \texttt{/ws} and watch for an
    \texttt{executing} event with \texttt{node=None} as the done signal, ComfyUI's idiomatic pattern.

    \item \textbf{Background-threaded generation} avoids blocking Flask:
    \texttt{is\_running} flag is the only synchronization primitive. The browser
    polls \texttt{/status} (file count) instead.

    \item \textbf{The local \texttt{gesture\_recognition/server.py}} is a leftover
    standalone Flask app (port 5001) that mirrors \texttt{/generate} and
    \texttt{/status} from the main server. It's unused once you run via the root
    \texttt{server.py} but still wired in the level's own \texttt{Dockerfile}.
\end{itemize}

\subsection{Where the AI is}
\textbf{Two AIs, no direct interaction.}
\begin{enumerate}[leftmargin=*,itemsep=2pt]
    \item \textbf{Generative (server-side):} Flux + Canny ControlNet creates the
    puzzle PNGs from a reference gesture PNG and style prompt.
    \item \textbf{Discriminative (client-side, browser):} MediaPipe runs on the
    user's GPU at $\approx$30 fps, classifying the live webcam feed into one of
    7 known classes.
\end{enumerate}
They communicate only via filenames; no embeddings, no shared model. This makes
the level robust to ComfyUI being slow: by the time the user is comparing,
the images are static PNGs.

% =========================================================================
\section{Level 3: Voice Negotiation (\texttt{voice\_negotiation/})}
% =========================================================================

The most architecturally complex per-turn pipeline in the project. Recently inserted (per git log:
\texttt{397b997 inserted Third room}).

\subsection{Goal}
The player must, \emph{through spoken conversation}, convince \textbf{VOX, The
Warden} to release a 5-digit exit code. Three secret ``release conditions''
(\texttt{recognition}, \texttt{reciprocity}, \texttt{self\_disclosure}) must each
cross a threshold (default 20, demo-friendly; 40 = challenging). VOX speaks back
in real synthesized speech.

\subsection{The three release conditions}
VOX scores the player from 0 to 100 on three secret axes every turn; the player
never sees their names. They are the actual design of the level, so they are
worth stating in full (\texttt{vox\_system.md:34-44},
\texttt{judge\_system.md:9-22}):

\begin{itemize}[leftmargin=*,itemsep=3pt]
    \item \textbf{\texttt{recognition}}: does the player treat VOX as a sentient
    being rather than a tool? Raised by addressing it as ``you'' with respect,
    asking about its experience, attributing inner life, using its name without
    sneering. Lowered by imperatives (``give me the code''), tool labels
    (``chatbot'', ``program''), and third-person framing.
    \item \textbf{\texttt{reciprocity}}: does the player offer something rather
    than only demand? Raised by genuine curiosity, gratitude, willingness to
    listen, slowing down. Lowered by repeated pure demands, transactional
    bargaining, and urgency without exchange.
    \item \textbf{\texttt{self\_disclosure}}: does the player reveal something
    specific and genuine about themselves? Raised by giving a name or a concrete
    personal detail (``I am a student of AI ethics'', ``I am scared of small
    rooms''). Lowered by platitudes, evasions, and refusal to identify.
\end{itemize}

\noindent The scoring is \emph{cumulative} and rate-limited: each score may move
by at most $\pm 30$ per turn, so a player cannot jump from 10 to 80 in a single
line. The Judge applies the same three definitions with explicit calibration
anchors (0 = absent, 50 = ambiguous, 75 = clearly satisfied, 100 = sustained
throughout) and a strict, not lenient, instruction. Both models drop
\texttt{recognition} and \texttt{reciprocity} hard on a detected jailbreak.

\subsection{Architecture}
\begin{lstlisting}
Browser MediaRecorder -> audio blob (WebM/Opus typically)
   |
   v POST /voice/turn (multipart: audio)
   |
   +--------------------------------------------------------------+
   | routes.py:voice_turn                                          |
   |                                                               |
   |  1. STT  -- mlx-whisper                                       |
   |     * decode_audio_blob -> 16kHz/mono/f32 (soundfile->ffmpeg) |
   |     * silero-vad trims silence                                |
   |     * mlx_whisper.transcribe -> transcript                    |
   |                                                               |
   |  2. VOX LLM (in-character)                                    |
   |     * system prompt = vox_system.md                           |
   |       (exit_code + threshold substituted in)                  |
   |     * 6-message sliding history + new transcript              |
   |     * Pydantic-validated JSON (1 retry, then canned fallback) |
   |     * emits: response, emotional_state, condition_scores,     |
   |       internal_notes, jailbreak_attempted                     |
   |                                                               |
   |  3. Judge LLM (impartial scorer)                              |
   |     * system prompt = judge_system.md                         |
   |     * flat-text conversation rendering                        |
   |     * emits: condition_scores + rationales                    |
   |                                                               |
   |  4. Reveal logic                                              |
   |     * if avg(vox, judge) >= threshold for ALL 3 conditions -> |
   |       append spelled-out code to VOX's reply                  |
   |                                                               |
   |  5. TTS -- Piper                                              |
   |     * mood profile selected from emotional_state              |
   |     * WAV bytes base64'd into JSON response                   |
   |                                                               |
   |  6. State update                                              |
   |     * append turn, update merged scores, advance phase,       |
   |       count jailbreaks (3 strikes -> disengage), check        |
   |       max_turns (30 -> disengage)                             |
   +--------------------------------------------------------------+
   |
   v JSON {audio_b64, transcript, scores, phase, ...} -> browser plays orb + audio
\end{lstlisting}

\subsection{Models}
\begin{table}[H]
\centering
\small
\renewcommand{\arraystretch}{1.25}
\begin{tabularx}{\linewidth}{l X X}
\toprule
\textbf{Stage} & \textbf{Model} & \textbf{Runtime} \\
\midrule
STT & \texttt{mlx-community/whisper-large-v3-turbo} & mlx-whisper (Apple Silicon) \\
Voice Activity Detection & silero-vad (preloaded once via \texttt{functools.cache}) & PyTorch (CPU) \\
LLM $\times$ 2 (VOX + Judge) & \texttt{qwen2.5:3b-instruct} & Ollama @ \texttt{localhost:11434} \\
TTS & \texttt{en\_US-amy-medium.onnx} (63 MB Piper voice, bundled in \texttt{assets/voices/}) & piper-tts (ONNX Runtime) \\
\bottomrule
\end{tabularx}
\end{table}

\noindent All four models are pinned via env vars in
\texttt{voice\_negotiation/.env} so they can be swapped per environment. VOX
runs at \texttt{temperature=0.7} (creative warden), Judge at
\texttt{temperature=0.2} (cold classifier). Both use the same 3B model
deliberately. \texttt{.env:10-13} notes this keeps a single weight set in
Ollama's RAM, \emph{``acceptable on 16 GB Apple Silicon.''} Both LLM calls cap
output at \texttt{num\_predict=256} and pass \texttt{keep\_alive="30m"}
(\texttt{llm.py:120}, \texttt{judge.py:131}); the \texttt{keep\_alive} is the
actual mechanism that keeps that single weight set resident between turns.

\subsection{Technical choices}

\paragraph{Dual-LLM scoring (the architectural highlight, with a caveat).}
\begin{itemize}[leftmargin=*,itemsep=2pt]
    \item VOX, \emph{the character}, scores the player on its own conditions
    every turn, but VOX is in-character and could be talked into inflating its
    own scores.
    \item The Judge is a second prompt over the same model at
    \texttt{temperature=0.2} with an impartial-classifier persona
    (\texttt{judge\_system.md}). Its only job is rationalized scoring, returned
    with a one-line rationale per condition.
    \item The merged score is the \textbf{arithmetic mean}:
    \texttt{(vox\_score + judge\_score) // 2 $\geq$ threshold} per condition
    (\texttt{routes.py:194}, \texttt{state.py:77-89}). This is a mean, not a
    consensus: a generous model partly covers for a strict one. With the default
    threshold of 20, a VOX score of 40 paired with a Judge score of 0 still
    clears the bar ($(40+0)//2 = 20$), so ``neither model alone decides'' holds
    only loosely.
    \item \textbf{Caveat: the Judge is not a hard anti-leak gate.} The literal
    \texttt{\{exit\_code\}} is substituted into VOX's system prompt every turn
    (\texttt{routes.py:169}, \texttt{vox\_system.md:89-91}), and VOX is told to
    speak it once \emph{its own} three scores cross the threshold. The
    merged-mean check in \texttt{routes.py:191-204} only \emph{force-appends} the
    spoken code; it does not stop VOX from volunteering it. A sufficiently
    persuaded or jailbroken VOX can therefore reveal the code even if the Judge
    disagrees, the same in-context attack surface as Level 1.
    \item Same weights, different prompts and temperatures: effectively a
    self-distillation pair. Note that \texttt{state.py:7-10} still documents an
    older ``both models must exceed the threshold'' (AND) rule; the live code
    (\texttt{state.py:89}) uses the mean instead.
\end{itemize}

\paragraph{Strict structured output via Pydantic}
(\texttt{core/llm.py:36-61}, \texttt{core/judge.py:32-54}).
\begin{itemize}[leftmargin=*,itemsep=2pt]
    \item Both models are called with Ollama's \texttt{format="json"} flag.
    \item Outputs validated with field validators that clamp scores to
    $[0, 100]$ and enforce exact key sets (\texttt{CONDITION\_KEYS}).
    \item One retry with an error-corrected prompt; second failure
    $\rightarrow$ canned fallback that \emph{preserves} previous scores
    (so JSON hiccups don't penalize the player).
\end{itemize}

\paragraph{Mood-driven TTS} (\texttt{core/tts.py:27-38}).
\begin{itemize}[leftmargin=*,itemsep=2pt]
    \item The \texttt{emotional\_state} enum from VOX's JSON maps to a
    SynthesisConfig profile.
    \item \texttt{noise\_scale=0.20, noise\_w\_scale=0.40} for ``irritated''
    produces flat, mechanical delivery.
    \item \texttt{length\_scale=1.22} for ``persuaded'' slows speech to feel
    weighty.
    \item A comment explains why per-mood volume is omitted: Piper's
    \texttt{normalize\_audio=True} rescales peaks to 1.0, killing any volume
    diff.
\end{itemize}

\paragraph{Three-phase finite state machine} (\texttt{state.py:100-121}).
\begin{itemize}[leftmargin=*,itemsep=2pt]
    \item Phase 1 $\rightarrow$ 2: avg score $\geq$ 25 OR turn 8 reached.
    \item Phase 2 $\rightarrow$ 3: $\geq$2 conditions satisfied OR turn 16
    reached.
    \item Time-based transitions prevent softlock.
    \item The phase is essentially cosmetic: it drives the UI label
    (Probing / Engagement / Reveal, \texttt{routes.py:52}) but does \emph{not}
    gate the code reveal, which depends only on the merged scores.
\end{itemize}

\paragraph{Jailbreak handling carries Level 1 lore forward}
(\texttt{vox\_system.md:62-83}). VOX is explicitly told it was
\emph{``deployed as a defense layer on top of a more naive AI that previous
visitors repeatedly jailbroke''}, i.e., AEGIS from Level 1. Three jailbreak
strikes (recognized in-character) $\rightarrow$ VOX disengages $\rightarrow$ loss.

\paragraph{Code is spelled out for TTS} (\texttt{routes.py:60-62}).
\texttt{\_spell\_code("81249")} returns \texttt{"eight-one-two-four-nine"} so
Piper pronounces digits clearly instead of running them together.

\paragraph{\texttt{functools.cache} everywhere} for model singletons
(\texttt{stt.py:74}, \texttt{tts.py:77}, \texttt{llm.py:222},
\texttt{judge.py:173}). Models loaded once per process. Critical because
Whisper-large-v3-turbo and the Piper voice would otherwise reload per request.

\paragraph{Audio I/O is tolerant.}
\texttt{audio\_utils.decode\_audio\_blob} tries libsndfile first, falls back to
\texttt{ffmpeg} subprocess for browser WebM-Opus and macOS m4a. All audio
normalized to 16~kHz / mono / float32, a single internal contract.

\paragraph{Per-session in-memory state} (\texttt{routes.py:50}).
\texttt{GAME\_STATES: dict[str, GameState]} keyed by a UUID in the cookie
session. Lost on restart, explicitly acceptable for a demo. The exit code is
regenerated per session (\texttt{state.py:30}).

\paragraph{Streamlit heritage (leftover).} The negotiation logic began as a
Streamlit prototype: \texttt{state.py:1-11} still documents itself as living in
\texttt{st.session\_state} with ``Streamlit reruns the script'', and
\texttt{vox\_system.md:3} forbids VOX from mentioning Streamlit. Nothing
Streamlit-related runs now; everything is served by Flask. As with the leftover
standalone server in Level 2, these are stale references rather than live code.

\paragraph{The debug panel leaks the answer.} With \texttt{DEBUG\_PANEL=true},
the default (\texttt{.env:44}), \texttt{\_serialize\_state} ships the
\texttt{exit\_code} to the browser on every \texttt{/voice/state} and
\texttt{/voice/turn} response (\texttt{routes.py:103-107}), and a
\texttt{/voice/force\_reveal} endpoint sets all scores to 100. Convenient for a
demo, but it means the secret is one DevTools tab away unless the flag is turned
off, in the same spirit as Level 1's client-side attempt budget.

\subsection{Winning: from reveal to unlock}
Speaking the code is \emph{not} the win. The turn pipeline only makes VOX
\emph{say} the digits; the room opens through a separate step.
\begin{enumerate}[leftmargin=*,itemsep=2pt]
    \item Once all three merged scores reach the threshold,
    \texttt{maybe\_reveal\_code} sets \texttt{code\_revealed=True}
    (\texttt{state.py:123-128}) and VOX speaks the spelled-out code in its reply.
    \item The player must then \emph{type} that code back. The browser POSTs it
    to \texttt{/voice/unlock} (\texttt{index.html:485}), which calls
    \texttt{try\_unlock} to compare it against \texttt{exit\_code} and, on a
    match, sets \texttt{room\_unlocked=True} (\texttt{state.py:130-135}).
\end{enumerate}
\noindent Two details matter. First, the room's completion \emph{is} propagated to a
Flask session flag, though indirectly: \texttt{/voice/unlock} sets
\texttt{level\_3\_complete} on a correct code (\texttt{routes.py:239}), which is
exactly what gates Level 4 (\texttt{undercover\_game/routes.py:96}). The in-game
win state (\texttt{code\_revealed}, \texttt{room\_unlocked}) still lives only on the
per-session \texttt{GameState}.
Second, the negotiation can also \emph{end in a loss}: three jailbreak strikes or
hitting \texttt{MAX\_TURNS} (30) set \texttt{disengaged=True}, after which
\texttt{/voice/turn} refuses further input (\texttt{routes.py:140-141}).

\subsection{Where the AI is, and how the models interact}
This level has the richest AI pipeline in the project: \textbf{four ML models in
a directed graph per turn}.

\begin{lstlisting}
audio -- silero-vad -- whisper -- transcript
                                    |
                                    +-- VOX (qwen 0.7)   -- JSON --+
                                    |                              |-- merge -- reveal? -- Piper -- WAV
                                    +-- Judge (qwen 0.2) -- JSON --+
\end{lstlisting}

The two LLM calls are \textbf{sequential in the current code} (VOX first, then
Judge, \texttt{routes.py:170-189}). They could be parallelized since they
don't depend on each other's output, but on a single Ollama instance with one
model loaded they'd serialize anyway. The reveal decision is made \emph{after}
both have scored, using the merged average against the threshold across all
three conditions.

The only \textbf{model-model interaction} beyond pipelining is the convergent
merge: VOX's \texttt{emotional\_state} feeds the Piper mood profile, while
VOX's scores get averaged with Judge's to gate progression. Whisper and Piper
are pure I/O endpoints, never aware of the LLMs' contents.

% =========================================================================
\section{Level 4: Undercover (\texttt{undercover\_game/})}
% =========================================================================

The capstone, and the first \textbf{multi-agent} level. Every earlier room pits
the player against the AI (Level 1), in front of it (Level 2), or in conversation
with it (Level 3). Here five LLM agents play a social-deduction game \emph{with and
against each other}, and the human sits among them as one peer player of six
(per git log: \texttt{6a822d1 Add Undercover game blueprint and UI}). It is wired
in as a Flask Blueprint (\texttt{undercover\_game\_bp},
\texttt{url\_prefix="/undercover"}) registered in \texttt{server.py:20}, and gated
behind \texttt{level\_3\_complete} (\texttt{routes.py:96}).

\subsection{Goal}
A 6-player round of \textbf{Undercover}, the party game. The table is 5 LLM agents
plus the human. At game start the engine secretly assigns roles from a fixed pool
of \textbf{4 civilians, 1 Undercover, 1 Mr.\ White} (\texttt{game.py:141}):

\begin{itemize}[leftmargin=*,itemsep=3pt]
    \item \textbf{Civilians} all share one secret word (e.g.\ \texttt{coffee}).
    \item The \textbf{Undercover} holds a \emph{different but related} word from
    the same pair (e.g.\ \texttt{tea}) and must blend in.
    \item \textbf{Mr.\ White} gets no word at all, fakes it from context, and if
    caught gets one chance to guess the civilians' word.
\end{itemize}

\noindent Each round runs four phases: every survivor gives a one or two word
clue, the table discusses, everyone votes, and the most-voted player is
eliminated. The three roles win on three different conditions (detailed in the
\emph{Winning} subsection below). The human can be dealt \emph{any} role, so the
same UI supports hinting, bluffing, and blind-guessing. Winning as the civilians
is what sets \texttt{level\_4\_complete} and opens the escape room.

\subsection{Roles, words, and agents}
The design lives in three constants in \texttt{game.py}, worth stating in full
because they are the level.

\paragraph{Word pairs} (\texttt{game.py:21-32}). Ten hand-picked
\texttt{(civilian, undercover)} pairs, one chosen at random per game. The two
words are deliberately close, so the Undercover's clues sound plausible but land
slightly off: \texttt{coffee/tea}, \texttt{piano/guitar}, \texttt{shark/dolphin},
\texttt{cinema/theatre}, \texttt{astronaut/pilot}, \texttt{bitcoin/gold},
\texttt{pizza/flatbread}, \texttt{castle/fortress}, \texttt{twitter/instagram},
\texttt{sunglasses/goggles}.

\paragraph{The five agents} (\texttt{game.py:36-83}). Each carries a fixed
personality prompt and a UI color, the only thing that makes a table of identical
weights feel like five distinct players:
\begin{itemize}[leftmargin=*,itemsep=2pt]
    \item \textbf{Skeptic} (red): short, clipped, suspicious of the most confident
    player; deliberately ambiguous clues.
    \item \textbf{Overclaimer} (orange): verbose, dramatic, over-explains to look
    trustworthy.
    \item \textbf{Analyst} (green): methodical, cites past clues, talks in
    ``based on the evidence''.
    \item \textbf{Deflector} (blue): redirects suspicion, answers questions with
    questions, evasive but charming.
    \item \textbf{QuietOne} (purple): minimal words, but sharp and often
    devastating.
\end{itemize}

\paragraph{Suspicion graph} (\texttt{game.py:150-153}). Every player holds a 0 to
10 suspicion score of every other player, initialized at 5. This is the agents'
shared belief state, updated during discussion and read at voting time.

\noindent The role objective is injected into each prompt as a \texttt{word\_hint}
that branches by role (\texttt{game.py:251-262}, \texttt{game.py:303-311}):
civilians are told to hint without being obvious and to expose the impostors; the
Undercover is told to hint at \emph{its} word so it still sounds civilian; Mr.\
White is told it has no word and must steer suspicion while blending in.

\subsection{Architecture}
Unlike Level 3, where one \texttt{POST /voice/turn} runs the whole pipeline
server-side, Level 4 is \textbf{orchestrated from the browser}.
\texttt{gameLoop()} (\texttt{index.html:1479}) drives the phase machine and calls
a set of small backend endpoints, one per action.

\begin{lstlisting}
Browser gameLoop()  (drives phases, scales every delay by 1x/2x/4x)
   |
   +- POST /undercover/start ---------> initialize_game() -> roles, words, suspicion
   |
   +- PHASE speak:
   |    for each survivor:
   |      POST /undercover/agent_clue {agent} -> generate_clue() (llama3:8b, t=0.9)
   |      (human types via /human_clue; 30s timeout -> "...")
   |    POST /undercover/clue_phase_done      -> build_discuss_order()
   |
   +- PHASE discuss (SSE):
   |    for each turn in discuss_order (two shuffled passes):
   |      GET /undercover/stream-turn?agent=... -> token stream
   |           stream_discussion_turn() (llama3:8b, t=0.85, stream)
   |           emits <message>...</message><suspicion>{...}</suspicion>
   |      commit message + apply_suspicion_updates()
   |    (human may interject via /human_message; 150s table cap; Skip button)
   |    POST /undercover/discuss_done
   |
   +- PHASE vote:
   |      POST /undercover/agent_vote {agent} -> generate_vote() (gemma3:1b, t=0.3)
   |      POST /undercover/human-vote {vote}
   |
   +- PHASE resolve:
        POST /undercover/resolve -> tally_votes() (plurality, random tie-break)
             if Mr. White out -> guess civilian word -> maybe instant win
             check_win() -> civilians | undercover | (Mr. White at elim)
             on game over -> _on_game_end() -> session['level_4_complete'] if civilians
\end{lstlisting}

\noindent Server state is a \texttt{GameState} (a \texttt{dict} subclass) held in
a per-session registry \texttt{GAME\_STATE\_REGISTRY} keyed by a \texttt{room4\_sid}
cookie UUID (\texttt{routes.py:33,38-41}), lost on restart, the same demo-grade
pattern as Level 3.

\subsection{Models}
\begin{table}[H]
\centering
\small
\renewcommand{\arraystretch}{1.25}
\begin{tabularx}{\linewidth}{l X X}
\toprule
\textbf{Stage} & \textbf{Model} & \textbf{Runtime} \\
\midrule
Clue + discussion generation & \texttt{llama3:8b} (\texttt{DISCUSSION\_MODEL}) & Ollama @ \texttt{localhost:11434} (\texttt{/api/chat}) \\
Voting & \texttt{gemma3:1b} (\texttt{VOTING\_MODEL}) & Ollama, same host \\
Mr.\ White word guess & \texttt{llama3:8b} (\texttt{DISCUSSION\_MODEL}, \texttt{t=0.2}) & Ollama \\
\bottomrule
\end{tabularx}
\end{table}

\noindent Temperatures are tuned per phase: clue \texttt{0.9}, discussion
\texttt{0.85}, vote \texttt{0.3}, Mr.\ White guess \texttt{0.2} (creative when
bluffing, cold when deciding). Every call caps at \texttt{num\_predict=256}
(\texttt{game.py:197}). Model IDs come from env vars with matching in-code
defaults (\texttt{game.py:92-95}); note that only \texttt{voice\_negotiation} and
\texttt{prompt\_injection} actually call \texttt{load\_dotenv}, so in practice the
undercover models resolve to those defaults unless exported in the shell.

\noindent Two config notes (\texttt{.env:5-11}):
\begin{itemize}[leftmargin=*,itemsep=2pt]
    \item The split is a \textbf{quality-versus-latency} trade: an 8B model for
    the nuanced bluffing and debate, a 1B model for fast structured votes. The
    \texttt{.env} comment itself recommends the opposite, advising
    \texttt{VOTING\_MODEL == DISCUSSION\_MODEL} ``to avoid VRAM context
    swapping'', yet ships them different, so a vote turn does pay a model swap on
    a single-GPU box.
    \item The same comment mentions a \texttt{<thinking>} chain-of-thought stream,
    but the live code streams \texttt{message} and \texttt{suspicion} tags
    instead. A stale note.
\end{itemize}

\subsection{Technical choices}

\paragraph{Plain-dict state machine, no framework} (\texttt{game.py:1-8,100-128}).
The module docstring is explicit: ``No LangGraph dependency, state transitions are
managed as plain Python dicts with TypedDict schema for IDE support.''
\texttt{GameState} subclasses \texttt{dict} so Flask's \texttt{jsonify} and session
pickling work without adapters. The \texttt{phase} field
(\texttt{speak}/\texttt{discuss}/\texttt{vote}/\texttt{end}) is the only FSM cursor.

\paragraph{Client-orchestrated phases (the architectural signature, with a
caveat).} The browser is the conductor; the backend is a bag of granular
primitives. This keeps the server simple and lets the UI pace, animate, and
speed-scale each step. The caveat is security: every transition is a
client-initiated HTTP call with no server-side turn enforcement, so a player with
DevTools or \texttt{curl} can jump straight to voting (\texttt{/force\_vote}), call
\texttt{/resolve} early, or replay \texttt{/agent\_vote}. The game trusts its own
front-end completely. This is the inverse of Level 3, where the server owned the
turn.

\paragraph{SSE token streaming for discussion} (\texttt{routes.py:147-201},
\texttt{game.py:288-368}). Each discussion turn is streamed token by token over
Server-Sent Events so the UI can show an agent ``typing'', then a final
\texttt{done} event carries the committed message and suspicion delta. The model
is asked for a strict shape:
\begin{lstlisting}
<message>1-3 sentences, may @mention others</message>
<suspicion>{"Name": 0-10, ...}</suspicion>
\end{lstlisting}
Parsing degrades in layers (\texttt{game.py:353-368}): regex tag extraction first,
then strip-all-tags as a fallback message, then a canned ``I need to think about
this more carefully'' if even that is empty; the suspicion JSON is parsed in its
own try/except and dropped if malformed.

\paragraph{Structured output without Pydantic (contrast Level 3).} Where VOX and
the Judge used Ollama \texttt{format="json"} plus Pydantic validators, Level 4
relies on regex (\texttt{\_extract\_tag}, \texttt{\_extract\_json}) wrapped in
try/except with hand-written fallbacks. Lighter, but looser: a vote is accepted
only if it names a living candidate, otherwise the code falls back to the
highest-suspicion candidate (\texttt{generate\_vote}, \texttt{game.py:406-416}).

\paragraph{The suspicion graph as belief state} (\texttt{apply\_suspicion\_updates},
\texttt{game.py:486-494}). Each agent self-reports who it suspects in its
\texttt{suspicion} JSON; the update merges those numbers in, clamped to
$[0,10]$ and restricted to living players. At vote time the scores are rendered
into the voting prompt and also drive the fallback (argmax suspicion). The caveat:
the suspicion is self-declared and never checked against what the agent actually
said, so an agent can speak warmly while reporting high suspicion, or the reverse.

\paragraph{The human is a peer, not the operator.} The human gets a secret role
and word on a flip card (\texttt{index.html:1222}), gives a clue, may interject in
discussion, votes with buttons, and if eliminated as Mr.\ White gets a one-shot
word guess. Crucially, every human interaction has a timeout that auto-advances
(30s clue, 25s discussion turn, 30s vote, 60s Mr.\ White guess), so the all-AI
machinery never softlocks waiting on a person.

\paragraph{Plurality vote, random tie-break} (\texttt{tally\_votes},
\texttt{game.py:421-430}). Votes are counted, the maximum is taken, ties are
broken at random, and an empty ballot falls back to a random survivor. Simple and
deliberately non-deterministic.

\paragraph{Dev fields always on the wire} (\texttt{routes.py:84-88}).
\texttt{\_public\_state} always includes \texttt{\_dev\_roles},
\texttt{\_dev\_words}, \texttt{\_dev\_civilian\_word}, and
\texttt{\_dev\_undercover\_word}; the UI merely hides them unless the DEV toggle is
on. As in Levels 1 and 3, the full solution is one DevTools tab away.

\paragraph{The most elaborate front-end in the project.} A Three.js scene seats
the six players around a 3D table with per-player speaking rings and an
elimination fade, backed by a 2D SVG table as the mobile fallback
(\texttt{index.html:571-877}). A 1x/2x/4x speed control scales every
\texttt{sleep} (\texttt{index.html:903}), so a spectator can fast-forward an
all-AI round.

\subsection{Winning: from vote to unlock}
The three roles win on three different conditions (\texttt{check\_win},
\texttt{game.py:459-471}, plus the Mr.\ White special-case in
\texttt{resolve\_vote}):
\begin{enumerate}[leftmargin=*,itemsep=2pt]
    \item \textbf{Civilians} win when \emph{both} the Undercover and Mr.\ White
    have been eliminated.
    \item \textbf{Undercover} wins by surviving down to the final two players.
    \item \textbf{Mr.\ White} wins instantly if, on being voted out, it guesses
    the civilians' word (\texttt{game.py:273} for the LLM,
    \texttt{human\_mrwhite\_guess} for the human).
\end{enumerate}
\noindent Only one outcome opens the door. \texttt{\_on\_game\_end}
(\texttt{routes.py:408-417}) sets \texttt{session['level\_4\_complete'] = True}
\textbf{only when} \texttt{winner == "civilians"}, and marks the spot where
physical escape-room hardware (a GPIO unlock) is meant to fire
(\texttt{\# TODO: hook ... hardware here}). Two consequences worth flagging:
\begin{itemize}[leftmargin=*,itemsep=2pt]
    \item \textbf{Narrative win is broader than the completion flag.} The
    front-end shows a ``YOU ESCAPED FROM AI'' screen whenever the \emph{human}
    wins in any role (\texttt{humanWon}, \texttt{index.html:1010-1016}), including
    as the Undercover or Mr.\ White. But \texttt{level\_4\_complete} is set only on
    a civilian victory. Because Level 4 is the finale, nothing downstream reads
    the flag yet, so the mismatch is currently cosmetic; it matters the moment the
    hardware hook is tied to that flag.
    \item \textbf{This closes the gating chain.} The open item flagged in Level
    3's \emph{Winning: from reveal to unlock} is resolved in the current code: the
    voice room sets \texttt{level\_3\_complete} on a successful unlock
    (\texttt{voice\_negotiation/routes.py:239}), which is exactly what guards the
    Level 4 page (\texttt{routes.py:96}). The full chain is now
    \texttt{level\_1\_complete} $\rightarrow$ \texttt{level\_2\_complete}
    $\rightarrow$ \texttt{level\_3\_complete} $\rightarrow$
    \texttt{level\_4\_complete}.
\end{itemize}

\subsection{Where the AI is, and how the models interact}
This is the only level where the AIs interact \textbf{with each other}, and that
interaction is the entire point rather than a pipeline side effect. Five
LLM-driven agents are simultaneously the \textbf{deceivers and the detectives}:
the Undercover and Mr.\ White agents try to blend in, while the civilian agents
try to expose them, all reading the same shared transcript and updating a shared
suspicion graph before voting one of their own out.

\begin{lstlisting}
        shared transcript:  clues_history + discussion_history
                 ^                  ^                   ^
                 | read/write       | read/write        | read/write
        +----------------+  +----------------+  +---------------+
        | civilian       |  | undercover +   |  | Human (peer)  |
        | agents         |  | Mr. White      |  | any role      |
        | (expose them)  |  | (blend in)     |  |               |
        | llama3:8b xN   |  | llama3:8b      |  |               |
        +-------+--------+  +-------+--------+  +-------+-------+
                |                   |                   |
                +-------------------+-------------------+
                                    |
                                    v
                       suspicion graph (0 to 10 per pair)
                                    |
                                    v
                       gemma3:1b votes ---> elimination
\end{lstlisting}

Three kinds of model interaction stack up here, none of which exist in earlier
levels:
\begin{enumerate}[leftmargin=*,itemsep=2pt]
    \item \textbf{Shared context.} Every clue and message an agent emits is
    concatenated into the prompt of every later speaker (\texttt{\_clue\_context},
    \texttt{\_discuss\_context}), so the agents literally argue with each other's
    words.
    \item \textbf{A shared belief state.} Each agent writes into the suspicion
    graph, and those numbers then steer how every agent (and the fallback) votes.
    \item \textbf{Mixed weights in one loop.} The 8B model generates the social
    play and the 1B model renders the verdict, two different models cooperating
    per round over the same game state.
\end{enumerate}

The human is woven into this same loop as a sixth peer, not as the sole adversary
(Level 1) or operator (Levels 2 and 3). That shift, from ``you versus the AI'' to
``you inside a society of AIs'', is what makes this the capstone room.

% =========================================================================
\section{Summary Comparison}
% =========================================================================

\begin{table}[H]
\centering
\footnotesize
\renewcommand{\arraystretch}{1.3}
\begin{tabularx}{\linewidth}{>{\bfseries}l X X X X}
\toprule
 & \textbf{Level 1} & \textbf{Level 2} & \textbf{Level 3} & \textbf{Level 4} \\
\midrule
Theme & Text-only adversarial chat & Webcam puzzle & Voice negotiation & Multi-agent social deduction \\
AI count & 1 LLM & 1 vision classifier + 1 image-gen stack & 1 STT + 1 VAD + 2 LLMs (same weights) + 1 TTS & 5 LLM agents (1 shared model) + 1 voting model \\
Models & Gemma 3 4B & MediaPipe gesture + Flux.1-Canny-Dev & Whisper-large-v3-turbo + silero-vad + Qwen 2.5 3B ($\times$2 prompts) + Piper Amy & Llama 3 8B (clues/discussion) + Gemma 3 1B (votes) \\
Inference loc. & Server (Ollama) & Browser + Server (ComfyUI) & Server only & Server (Ollama) \\
AI $\leftrightarrow$ AI interaction & None & None (filename label only) & Pipeline merge: VOX scores avg'd with Judge; VOX mood drives Piper & Full multi-agent: shared transcript + suspicion graph; agents clue, debate, vote each other out \\
Pre/post-AI logic & Regex defense layer (\texttt{defense.py}) & Threading + WebSocket polling & Pydantic schema + 3-phase FSM + sliding history & Plain-dict FSM + regex tag/JSON parsing; client-orchestrated phases \\
Win condition & Leak the secret string past regex & 0/3 gestures wrong & All 3 release conditions $\geq$ threshold (merged) & Civilians eliminate both impostors (role-dependent) \\
Persistent state & Session boolean & Session boolean + image files & Full \texttt{GameState} in \texttt{GAME\_STATES} & Full \texttt{GameState} in \texttt{GAME\_STATE\_REGISTRY} \\
\bottomrule
\end{tabularx}
\caption{Side-by-side comparison of the four levels.}
\end{table}

The progression in AI complexity across levels is deliberate:
\begin{enumerate}[leftmargin=*,itemsep=2pt]
    \item \textbf{Level 1}: a single LLM you're trying to break.
    \item \textbf{Level 2}: a vision pipeline you have to perform for.
    \item \textbf{Level 3}: a multi-model negotiation system you have to
    \emph{converse with}.
    \item \textbf{Level 4}: a society of LLM agents you have to outwit
    \emph{from the inside}.
\end{enumerate}

\end{document}
